Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-15 trunk/papers/icsoc2010/paper_sec_catalogue.tex
updating catalogue section
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@886 d8b0c59b-6544-0410-94d9-83a5658a058e

The area of web service publication and discovery has been subject for a lot of research since the very beginning the concept was coined. The current state of the art provides several solutions and strategies which providers and consumers may take advantage of. However, as explained in previous sections, a large number of them suffer from limited syntactic-based descriptions and a simple keyword-based search, and the gap between discovery and consumption is an obstacle for their usage by a non-technical common user. In order to lighten the issue, this paper presents yet another publishing platform, permitting any enterprise or individual to publish their public domain web services, with an enhanced semantic search based on the definition of the services, and serving ``web service wrappers'' for an easy consumption in any web application.

@@

The main difference of this platform with regards to the state of the art is that it is clearly targeting a different kind of user, and covers many deficiencies others tools does not tackle with. As a briefly overview, the platform being presented:

\begin{itemize}
  \item allows functional discovery through web services pre and postconditions;
	\item serves web services wrappers ready-to-consume in any web application;
	\item provides advanced search capabilities, based on the service formal definition and inferences extracted from it;
	\item supports managing its resources via its RESTful API;
	\item a SPARQL endpoint to access directly to the data allowing advanced queries;
	\item offers web services as Linked Data;
	\item follows well-known best practices for publishing data on the web;
	\item supports content negotiation so the different clients may retrieved the information in JSON, RDF/XML, RDF/N3 or a human-readable HTML version;
\end{itemize}

This platform was intended and it is being used as part of the storyboard tool of the FAST platform~\cite{hoyer2009fast}, and it communicates with other components through its RESTful API, using JSON for the input of the requests. This paper will focus on the functionality regarding web services publication and discovery, and the process to publish any third-party web service into the platform. This process requires two steps: (i) generation of the wrapper (see Sec. \ref{sec:wrapping_web_services}, and (ii) creation of the resource in the publishing platform. The following is an example of part of a request sent to create a new wrapper into the platform (for the sake of clarity, some parts of the request have been omitted, but the main idea is shown):

@@

The enriched search capabilities are supported by the definition of pre and postcondition. It allows to define the inputs and outputs of the services using concepts from any ontology, and find web services which match and hence is able to communicate with other web services or building block. The concepts of pre/postconditions were highly influenced by WSMO \cite{roman2005}, make it simpler and implemented in RDFS for a better performance. The model used to define the web service wrappers and the ontology created are detailed in Section~\ref{ssec:ontology}.

>>>>

The area of web service publication and discovery has been subject for a lot of research since the very beginning the concept was coined. The current state of the art provides several solutions and strategies which providers and consumers may take advantage of. However, as explained in previous sections, a large number of them suffer from limited syntax-based descriptions and simple keyword-based search, and the gap between discovery and consumption is an obstacle for their usage by non-technical end-users. In order to improve this issue, this paper presents a novel publishing platform, permitting any enterprise or individual to publish their public domain web services, with an enhanced semantic search based on the definition of the services, and serving web service wrappers for easy consumption in web applications.

@@

The main difference of this platform with regards to the state of the art is that it is targeting a different kind of user, and covers many deficiencies others tools do not tackle. As a brief overview, the platform being presented:

\begin{itemize}
  \item allows functional discovery through web service pre- and post-conditions;
	\item serves web services wrappers ready to consume in web applications;
	\item provides advanced search capabilities, based on the formal service definition and inferences extracted from it;
	\item supports managing its resources via its RESTful API;
	\item offers a SPARQL endpoint, giving direct access to the data through complex queries;
	\item offers web service descriptions as linked data;
	\item follows well-known best practices for publishing data on the web;
	\item supports content negotiation so that different clients may retrieve information in their preferred format, choosing from JSON, RDF/XML, RDF/N3 or a human-readable HTML version.
\end{itemize}

This platform was intended and it is being used as part of the storyboard tool of the FAST platform~\cite{hoyer2009fast}, and it communicates with other components through its RESTful API, using JSON for the input of the requests. This paper will focus on the functionality regarding web service publication and discovery, and the process to publish any third-party web service into the platform. This process requires two steps:
\begin{inparaenum}[(i)]
	\item generation of the wrapper (see Sect. \ref{sec:wrapping_web_services}), and 
	\item creation of the resource in the publishing platform. 
\end{inparaenum}
The following is an example of part of a request sent to create a new wrapper into the platform (for the sake of clarity, some parts of the request have been omitted, but the main idea is shown):

@@

The enriched search capabilities are supported by the definition of pre- and post-conditions. They allows to define the inputs and outputs of the services and other building blocks using concepts from any ontology, and in this way to find web services or other building blocks which match each other and can therefore be integrated. The concepts of pre-/post-conditions were strongly influenced by WSMO~\cite{roman2005}, simplified and implemented in RDFS for better live performance. The model used to define the web service wrappers and the ontology created are described in more detail in Sect.~\ref{ssec:ontology}.
